---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.path = "man/figures/README-", eval = FALSE,
  message = FALSE, warning = FALSE, error = FALSE, tidy = TRUE
)
```

# apputils

[![Travis-CI Build Status](https://travis-ci.org/leonawicz/apputils.svg?branch=master)](https://travis-ci.org/leonawicz/rapputils)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/leonawicz/apputils?branch=master&svg=true)](https://ci.appveyor.com/project/leonawicz/apputils)
[![Coverage Status](https://img.shields.io/codecov/c/github/leonawicz/apputils/master.svg)](https://codecov.io/github/leonawicz/apputils?branch=master)

`apputils` is an R package containing common utilty functions, settings and references for development use across multiple Shiny apps,
It has a `shinydashboard` focus. `apputils` is a satellite member of the SNAPverse collection of R packages. 
It supports other satellites in the verse, including `maputils` and `snaputils`.

## Functionality

Package functionality and areas of support covered by `apputils` include:

* Overrides of `shinydashboard::valueBox`, `shinydashbaord::infoBox` and `shiny::icon` that support the use of local thumbnails images.
* Stat boxes: special type of value or info boxes for common statistics using a collection of icons provided by the package.
* Adjusted CSS styles and integration with packages like `rintrojs` and `shinytoastr` for interactive tours and toast messages.
* Functions for including app information widgets such as citations, contact info, frequently asked questions and more.
* Encapsulation of working with data frames in server.R in specific contexts and use cases to simplify code.
* Wrappers around specific use cases for Leaflet maps, data tables, and general plotting in apps.
* Helper functions for dynmaic reports.

## Installation and bug reporting

Install the latest development version from github with

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("leonawicz/snaputils")
```

Please file a minimal reproducible example of any clear bug at [github](https://github.com/leonawicz/apputils/issues).

## Reference

[Package reference and function documentation](https://leonawicz.github.io/apputils/)
